### 2016-10-12 R/ITHIM.Rmd
compute <- TRUE
First attempt at new analysis
Changed the way ITHIM.default is treated.

```{r subset, eval = compute, fig.width = 10, echo = FALSE}
NHTS.person <- subset( NHTS.person, MSA == TRUE ) # & HHSTATE %in% c("CA","TX","NY","FL","VA","NC","AZ"))
NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"))
saveRDS(NHTS, file = "./data/NHTS.rds")
```

@@

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
upper <- 10; length <- 5; wd <- upper/length;

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")
ITHIM.default <- updateITHIM(ITHIM.default, "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIM.default, "cv", 3.0288)
ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", (1:99)/100)

@@

for (HHSTATE in c("CA","TX","NY","FL","VA","NC","AZ")){
    ITHIMList[[HHSTATE]] <- ITHIM.default
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "muwt", muwtList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "muct", muctList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "Rwt", RwtList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "Rct", RctList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "GBD", ITHIM.national$parameters$GBD)
  }

@@

  for (HHSTATE in c("CA","TX","NY","FL","VA","NC","AZ")){
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "muNonTravel", muNonTravel)
  }

@@

DALYsTotal <- within(DALYsTotal, {
  State <- factor(State, levels = c("NC","TX","VA","FL","AZ","NY","CA"))
})

@@

```{r ITHIMObjsQuintiles, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
DALYsTotal2 <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")
ITHIM.default <- updateITHIM(ITHIM.default, "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIM.default, "cv", 3.0288)
ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", seq(1, 9, by = 2)/10 )

@@

DALYsTotal2 <- within(DALYsTotal2, {
  State <- factor(State, levels = c("NC","TX","VA","FL","AZ","NY","CA"))
})

@@

@@

# Appendix

>>>>

```{r subset, eval = compute, fig.width = 10, echo = FALSE}
NHTS.person <- subset( NHTS.person, MSA == TRUE )
NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"))
saveRDS(NHTS, file = "./data/NHTS.rds")
```

@@

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
stateVec <- c("CA","TX","NY","FL") #c("CA","TX","NY","FL","VA","NC","AZ")
stateVecOrdered <- c("TX","FL","NY","CA") #c("NC","TX","VA","FL","AZ","NY","CA")

upper <- 10; length <- 5; wd <- upper/length;

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")
ITHIM.default <- updateITHIM(ITHIM.default, "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIM.default, "cv", 1.65)
ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", (1:99)/100)

@@

for (HHSTATE in stateVec){
    ITHIMList[[HHSTATE]] <- ITHIM.default
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "muwt", muwtList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "muct", muctList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "Rwt", RwtList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "Rct", RctList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "GBD", ITHIM.national$parameters$GBD)
  }

@@

  for (HHSTATE in stateVec){
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "muNonTravel", muNonTravel)
  }

@@

DALYsTotal <- within(DALYsTotal, {
  State <- factor(State, levels = stateVecOrdered)
})

@@

```{r ITHIMObjsQuintiles, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
DALYsTotal2 <- data.frame()
ITHIMList <- list()

#ITHIM.default <- createITHIM(vision = "baseline", region = "national")
#ITHIM.default <- updateITHIM(ITHIM.default, "cvNonTravel", 3)
#ITHIM.default <- updateITHIM(ITHIM.default, "cv", 1.65)

ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", seq(1, 9, by = 2)/10 )

@@

DALYsTotal2 <- within(DALYsTotal2, {
  State <- factor(State, levels = stateVecOrdered)
})

@@

```{r methodsPaper, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = phi, warning = FALSE, message = FALSE, echo = FALSE}

ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", (1:99)/100)

```
# Appendix

@@
